A Spatial AR System for Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-07-11 paper/elsarticle/elsarticle-template.tex
paper

An early spatial AR system for planar scenes using a projector with a steerable mirror is the IBM Everywhere Displays prototype of Pinhanez \cite{pinhanez2001everywhere}, yet compute the warps applied to imagery to be projected manually. Rather than rely on a steerable mirror to support spatial AR to multiple locations using a single projector, some works mount the projector and a camera on a rigid rig and subject the rig to motion \cite{ehnes2004projected,borkowski2004spatial}. Steering only a mirror, however, places humbler requirements on the system from a hardware standpoint than if an entire camera-projector rig is to be subject to steering. ...

>>>>

An early spatial AR system for using a projector with a steerable mirror is the IBM Everywhere Displays prototype of Pinhanez \cite{pinhanez2001everywhere}, yet carry out keystone correction manually. Rather than rely on a steerable mirror to support spatial AR to multiple locations using a single projector, some works mount the projector and a camera on a rigid rig and subject the rig to motion \cite{ehnes2004projected,borkowski2004spatial,butz2006applying}. Steering only a mirror, however, places humbler requirements on the system from a hardware standpoint than if an entire camera-projector rig is to be subject to steering. ...
